---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
antismash_bgcs_crc <- read.table(file = 'all10_output.tsv', sep = '\t')
families_present_crc10 <- antismash_bgcs_crc %>% count(V2)
#families_present_crc10 <- distinct(data.frame(antismash_bgcs_crc$V2))
write.table(families_present_crc10, file='crc_10families.tsv', quote=FALSE, sep='\t', col.names = NA)
pie(families_present_crc10$n, labels = families_present_crc10$V2)

attach(antismash_bgcs_crc)

```
```{r}
ordered_families_crc10 <- families_present_crc10 %>% arrange(desc(n))
ordered_families_crc10
clean <- ordered_families_crc10 %>% rename(Cluster_type = V2, Cluster_count = n)
clean
write.table(clean, file='clean_crc_10families.tsv', quote=FALSE, sep='\t', col.names = NA)
#get sample avergae in each fil
```

```{r}

ggplot(data=antismash_bgcs_crc, aes(x=V2, y=1:547)) + 
  geom_bar(stat = "identity")
```


#ggplot(data = antismash_bgcs_crc, aes(x = "", y = antismash_bgcs_crc$n, fill = V2)) + 
  #geom_bar(stat = "identity") + 
#  coord_polar("y")

ggplot(data = antismash_bgcs_crc, aes(x = "", y ='n', 
                           fill=V2 )) + 
  geom_bar(stat = "identity") + 
  labs(title = "CRC Samples 10x BGCs present and quantitiy") +
  coord_polar("y") +
  theme_void()

# Barplot
bp <- ggplot(antismash_bgcs_crc, aes(x="", y='n', fill=V2))+
geom_bar(width = 1, stat = "identity")
bp
pie <- bp + coord_polar("y", start=0)
pie

# Basic box plot from data frame
#qplot('V2', 'n', data = antismash_bgcs_crc, 
#      geom= "boxplot", fill = V2)

#ggplot(data = antismash_bgcs_crc, aes(x='V2', y=seq(1, 100, by=2), fill='n')) + 
 #   geom_boxplot()

# Violin plot
#qplot(sex, weight, data = wdata, geom = "violin")
# Dot plot
#qplot(sex, weight, data = wdata, geom = "dotplot",
#      stackdir = "center", binaxis = "y", dotsize = 0.5)


# Plot the bar chart 
#barplot(antismash_bgcs_crc$n, lab="BGC",ylab="Quantity Detected",col="blue",
#main="CRC BGC chart",border="black")

ggplot(antismash_bgcs_crc, aes(x=V2, y=n)) + 
  geom_bar(stat = "identity")
#ax = antismash_bgcs_crc.plot.bar(x='V2', y='n', rot=0)

#barplo

